Annotation Guideline for \textsc{Tweebank v2}

### 2018-04-13 guideline.tex
update

@@

\paragraph{Group name.}
Mentions about groups (music group, sport group, and etc.) are common in tweets.
The names of music group can present complex syntactic structures,
e.g. \underline{\textit{One Direction}}, \underline{\textit{Zac Brown Band}},
and \underline{\textit{Rico Riders}}.
In this guideline, we propose to analyze the in the same way as
person name, using \textit{flat} to the left-most token.

There are several group names presented in \textsc{Tweebank v2}. Here is a comprehensive list:
\textit{One Direction, Super Junior, 
	Higher Authority,
	Eagles of Death Mental, 
	*5 Second of Summer*,
	Carolina Panthers, Rico Riders, Manchester United, Real Madrid,
	49ers, Patriots, Heat, Celtics
}.

@@

\paragraph{Product name.}
We analyze product name as a normal nominal phrase.
Thus, tokens like \textit{shoulder bag} are analyzed as \texttt{NOUN} rather than \texttt{PROPN}.
\begin{itemize}
	\item Apple Music, Didi Chuxing. Zapata Beer
	\item Asus Gaming PC
	\item Louis Vuitton Monogram Marelle Shoulder Bag
	\item Puzzle Sharks
\end{itemize}

@@

\paragraph{Organization name.} 
We analyze organization name as a normal noun phrase.
We use \texttt{PROPN} as the POS tag.
\begin{itemize}
	\item Clinton Global Initiative University
	\item Santander UK
\end{itemize}

\paragraph{Event name.}
\begin{itemize}
	\item Bush Tax Cuts
	\item Down to Lunch
	\item Stanley Cup
\end{itemize}

>>>>

Truncated URL.

@@

\paragraph{Group name.}
Mentions about groups (music group, sport group, and etc.) are common in tweets.
The names of music group can present complex syntactic structures,
e.g. \underline{\textit{One Direction}}, \underline{\textit{Zac Brown Band}},
and \underline{\textit{Rico Riders}}.
In this guideline, we propose to analyze the syntax using \textit{compound}.
However, if there is \texttt{ADP} in the group name like \textit{Eagles of Death Mental}, we analyze them as a normal noun phrase.

There are several group names presented in \textsc{Tweebank v2}. Here is a comprehensive list:
\textit{One Direction, Super Junior, 
	Higher Authority,
	Eagles of Death Mental, 
	*5 Second of Summer*,
	Carolina Panthers, Rico Riders, Manchester United, Real Madrid,
	49ers, Patriots, Heat, Celtics,
	Mariners,
	Nature Republic,
	The weekend,
	Kiss Daniel,
	Yung 4,
	Doncaster Phoenix,
	West Hartlepool
}.

@@

\paragraph{Product name.}
We analyze product name as a normal nominal phrase.
Thus, tokens like \textit{shoulder bag} are analyzed as \texttt{NOUN} rather than \texttt{PROPN}.
\begin{itemize}
	\item Apple Music, Didi Chuxing. Zapata Beer
	\item Asus Gaming PC
	\item Louis Vuitton Monogram Marelle Shoulder Bag
	\item Puzzle Sharks
	\item After School Snack
	\item CARVIN BX250 250 W Micro Bass Guitar Amp Amplifier Head / Compressor
	\item Lake Wind Advisory
	\item CARVIN BX250
	\item Australian Gelato
	\item Pokemon GO
	\item Windows live
\end{itemize}

@@

\paragraph{Organization name.} 
We analyze organization name as a normal noun phrase.
We use \texttt{PROPN} as the POS tag.
We analyze most of the organization names as compound.
But for cases like \textit{Santander UK}.
\begin{itemize}
	\item Clinton Global Initiative University
	\item Santander UK
	\item Parag Milk Foods
	\item Alabama Banking Department
	\item Lady Tattoo Studio
	\item Hartlepool Mail
	\item Big East
\end{itemize}

\paragraph{Event name.}
\begin{itemize}
	\item Bush Tax Cuts
	\item Down to Lunch
	\item Stanley Cup
	\item The CJUSD District College and Career Fair
	\item \#AV/IT Leadership Summit
	\item FA Cup
\end{itemize}
